\textbf{Evalution of binary classification pipelines and methods for 16S rRNA gene data}

### 2018-11-09 results/tables/Table3.Rmd
tables generated as seperate pdf

```{r table_2, echo=FALSE, results='asis'}
######################################################################
# We load a param_grid.scv file to make our Table 2 and 3. This file has the information of the ranges of the optimized hyper-parameters for each model.

@@

# We will generate a Table for non-tree based models that shows C(penalty) and gamma hyperparameters.
######################################################################

################ Non-tree based model parameters ##############
linear_param_range <- read.table('../../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  ## only select Logistic Regression and SVM model columns
  select(1:17) %>% 
  ## only select C (penalty) and gamma rows as parameters
   slice(1:2)

#------------------------Table 2 generation------------------------#
Table2 <- kable(linear_param_range, 
                "latex", 
                caption = "Table 2. The range of optimized hyper-parameters for logistic regression and support vector machines.", 
                booktabs = T, 
                col.names = NULL, 
                linesep = "") %>%
  # latex options make table to be condensed
  # table itseld if left aligned
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"), 
                position = "left") %>% 
  # the column names are removed when the file is read so I put headers above the grouped/replicated modeling method for
  add_header_above(c("Parameter", "L2 Logistic" = 4, "L1 SVM Linear" = 4, "L2 SVM Linear " = 3, "SVM RBF"=5), bold=TRUE) %>% 
  # Put a left border to seperate above header lines
  column_spec(2, border_left = T) %>%
  column_spec(6, border_left = T) %>% 
  column_spec(10, border_left = T) %>% 
  column_spec(13, border_left = T)

Table2
```

>>>>

```{r table_3, echo=FALSE, results='asis'}
######################################################################
# We load a param_grid.scv file to make our Table 2 and 3. This file has the information of the ranges of the optimized hyper-parameters for each model.

@@

# We will generate a Table for tree based models that show all the hyperparameters used for it. 
######################################################################

################ Tree based model parameters ##############
tree_param_range <- read.table('../../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  ## only select Logistic Regression and SVM model columns
  select(1, 18:29) %>% 
  ## select all rows except C (penalty) and gamma for parameters
  slice(3:9)

#------------------------Table 3 generation------------------------#
Table3 <- kable(tree_param_range, 
                "latex", 
                caption = "Table 3. The range of optimized hyper-parameters for tree based classification algorithms.", 
                booktabs = T, 
                col.names = NULL, 
                linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down", "hold_position"), 
              position = "left", font_size=6) %>% 
  add_header_above(c("Parameter", "Random Forest"=5, "Decision Tree"= 4, "XGBoost"=3 ), bold=TRUE) %>% 
  column_spec(2, border_left = T) %>% 
  column_spec(7, border_left = T)%>% 
  column_spec(11, border_left = T)

Table3
```

### 2018-11-09 submission/manuscript.Rmd
running title
tables generated as seperate pdf

```{r table_1_models, echo=FALSE, results='asis'}
######################################################################
# We load a model parameters file to make our Table 1. Model parameters file has the information of optimized hyper-parameters, pre-processing and cross-validation methods and software implementation for all the classification algorithms.

# This file is hand-made. Therefore needs to be changed manually if new information wants to be added or information needs to be changed. 
######################################################################
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t') %>% 
   select(Method, Parameter, Cross.Validation, Epochs, Scaler, Sklearn.Function) %>% 
  rename("Cross Validation"="Cross.Validation") %>%
  rename("Epoch"="Epochs") %>%
  rename("Sklearn Function"="Sklearn.Function")

#------------------------Table 1 generation------------------------#

Table1 <- kable(model_param, 
                "latex", 
                caption = "Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms.", 
                booktabs = T, 
                linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down"), 
              position = "left") %>%  
 column_spec(1, width="10em") %>%
  column_spec(2, width="8em") %>% 
  column_spec(3, width="9em") %>%
  column_spec(5, width="5em") %>% 
  row_spec(1:7, align="l") %>% 
  row_spec(0,bold=TRUE)
```

```{r table_2_3_params, echo=FALSE, results='asis'}
######################################################################
# We load a param_grid.scv file to make our Table 2 and 3. This file has the information of the ranges of the optimized hyper-parameters for each model.

# This file is generated from model_selection.py that is used to define model parameters for main.py. Therefore any changes to those files would allow us to represent them in the tables automatically.

# 1) First we will generate a Table for non-tree based models that shows C(penalty) and gamma hyperparameters.

# 2) Second we will generate a Table for tree based models that show all the hyperparameters used for it. 
######################################################################

################ Non-tree based model parameters ##############
linear_param_range <- read.table('../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  ## only select Logistic Regression and SVM model columns
  select(1:17) %>% 
  ## only select C (penalty) and gamma rows as parameters
   slice(1:2)

#------------------------Table 2 generation------------------------#
Table2 <- kable(linear_param_range, 
                "latex", 
                caption = "The range of optimized hyper-parameters for logistic regression and support vector machines.", 
                booktabs = T, 
                col.names = NULL, 
                linesep = "") %>%
  # latex options make table to be condensed
  # table itseld if left aligned
  kable_styling(latex_options = c("striped", "scale_down"), 
                position = "left") %>% 
  # the column names are removed when the file is read so I put headers above the grouped/replicated modeling method for
  add_header_above(c("Parameter", "L2 Logistic" = 4, "L1 SVM Linear" = 4, "L2 SVM Linear " = 3, "SVM RBF"=5), bold=TRUE) %>% 
  # Put a left border to seperate above header lines
  column_spec(2, border_left = T) %>%
  column_spec(6, border_left = T) %>% 
  column_spec(10, border_left = T) %>% 
  column_spec(13, border_left = T)

################ Tree based model parameters ##############
tree_param_range <- read.table('../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  ## only select Logistic Regression and SVM model columns
  select(1, 18:29) %>% 
  ## select all rows except C (penalty) and gamma for parameters
  slice(3:9)

#------------------------Table 3 generation------------------------#
Table3 <- kable(tree_param_range, 
                "latex", 
                caption = "The range of optimized hyper-parameters for tree based classification algorithms.", 
                booktabs = T, 
                col.names = NULL, 
                linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down"), 
              position = "left", font_size=6) %>% 
  add_header_above(c("Parameter", "Random Forest"=5, "Decision Tree"= 4, "XGBoost"=3 ), bold=TRUE) %>% 
  column_spec(2, border_left = T) %>% 
  column_spec(7, border_left = T)%>% 
  column_spec(11, border_left = T)
```
\vspace{35mm}

Running title: INSERT RUNNING TITLE HERE

>>>>

Running title: Machine learning methods in microbiome studies

### 2018-11-09 submission/manuscript.tex
tables generated as seperate pdf

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={NAME OF THIS STUDY},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{\textbf{NAME OF THIS STUDY}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

@@

Running title: INSERT RUNNING TITLE HERE

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Evalution of binary classification pipelines and methods for 16S rRNA gene data},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{\textbf{Evalution of binary classification pipelines and methods for 16S
rRNA gene data}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

@@

Running title: Machine learning methods in microbiome studies
